---
title: "Investigating COVID-19 Virus Trends"
author: "yunsanghwang"
date: '2020 7 21 '
output: html_document
---

This is a project about the covid19 virus.

```{r}
getwd()
setwd("C:/Users/yunsang/downloads")
library(readr)
library(tibble)
library(dplyr)
covid_df <- read_csv("covid19.csv")
```

How much data is there?

```{r}
dim(covid_df)
```
```{r}
vector_cols <- colnames(covid_df)
vector_cols
```
Date: Date
Continent_Name: Continent names
Two_Letter_Country_Code: Country codes
Country_Region: Country names
Province_State: States/province names; value is All States when state/provincial level data is not available
positive: Cumulative number of positive cases reported.
active: Number of actively cases on that day.
hospitalized: Cumulative number of hospitalized cases reported.
hospitalizedCurr: Number of actively hospitalized cases on that day.
recovered: Cumulative number of recovered cases reported.
death: Cumulative number of deaths reported.
total_tested: Cumulative number of tests conducted.
daily_tested: Number of tests conducted on the day; if daily data is unavailable, daily tested is averaged across number of days in between.
daily_positive: Number of positive cases reported on the day; if daily data is unavailable, daily positive is averaged across number of days in.
```{r}
head(covid_df)
```

```{r}
glimpse(covid_df)
```


I'll filter the rows related to "All States" from the Province_State column and remove the Province_State column from covid_df dataframe.
```{r}
covid_df_all_states <- covid_df %>% filter(Province_State == "All States") %>% select(-Province_State)
```



the columns with cumulative numbers
```{r}
covid_df_all_states_daily <- covid_df_all_states %>% select(Date, Country_Region, 
                                                            active, hospitalizedCurr, 
                                                            daily_tested, daily_positive)
```




```{r}
covid_df_all_states_daily_sum <- covid_df_all_states_daily %>% 
  group_by(Country_Region) %>%
  summarize(tested = sum(daily_tested),
            positive = sum(daily_positive),
            active = sum(active),
            hospitalized = hospitalizedCurr) %>%
  arrange(desc(tested))
covid_df_all_states_daily_sum
```



```{r}
covid_top_10 <- head (covid_df_all_states_daily_sum, 10) 
covid_top_10
```
Identifying the Highest Positive Against Tested Cases
```{r}
countries <- covid_top_10$Country_Region
tested_cases <- covid_top_10$tested
positive_cases <- covid_top_10$positive
active_cases <- covid_top_10$active
hospitalized_cases <- covid_top_10$hospitalized
```



```{r}
names(positive_cases) <- countries
names(tested_cases) <- countries
names(active_cases) <- countries
names(hospitalized_cases) <- countries
```



```{r}
sum(positive_cases)
mean(positive_cases)
positive_cases/sum(positive_cases)
```


```{r}
positive_cases / tested_cases
```

```{r}
positive_tested_top_3 <- c("United Kingdom" = 0.11, "United States" = 0.10, "Turkey" = 0.08)
```

```{r}
united_kingdom <- c(0.11, 1473672, 166909, 0, 0)
united_states <- c(0.10, 17282363, 1877179, 0, 0)
turkey <- c(0.08, 2031192, 163941, 2980960, 0)
```

```{r}
covid_mat <- rbind(united_kingdom, united_states, turkey)
```


```{r}
colnames(covid_mat) <- c("Ratio", "tested", "positive", "active", "hospitalized")
covid_mat
```


```{r}
question <- "Which countries have had the highest number of positive cases against the number of tests?"
answer <- c("Positive tested cases" = positive_tested_top_3)

```



```{r}
datasets <- list(
  original = covid_df,
  allstates = covid_df_all_states,
  daily = covid_df_all_states_daily,
  top_10 = covid_top_10
)
```


```{r}
matrices <- list(covid_mat)
vectors <- list(vector_cols, countries)
```


```{r}
data_structure_list <- list("dataframe" = datasets, "matrix" = matrices, "vector" = vectors)
covid_analysis_list <- list(question, answer, data_structure_list)
covid_analysis_list[[2]]
```

