---
title: "analyzing CIA Factbook"
author: "Yunsang Hwang"
date: "2020년 3월 14일"
output: html_document
---

read library
```{r}
library(RSQLite)
library(DBI)
library(tidyr)
library(ggplot2)
library(purrr)
library(readxl)
library(dplyr)
```


overview data
```{r}
conn <- dbConnect(SQLite(), 'factbook.db')

query <- "SELECT * FROM facts LIMIT 5"
result <- dbGetQuery(conn, query)
```


Let's find out the maximum and minimum values of population and population growth rate.
```{r}
query_2 <- "SELECT MIN(population), MAX(population), 
                   MIN(population_growth), MAX(population_growth) FROM facts"
result_2 <- dbGetQuery(conn, query_2)
```

```{r}
query_3 <- "SELECT * FROM facts WHERE population == (
                                                     SELECT MAX(population) FROM facts);"
query_4 <- "SELECT * FROM facts WHERE population == (
                                                     SELECT MIN(population) FROM facts);"
result_3 <- dbGetQuery(conn, query_3)
result_4 <- dbGetQuery(conn, query_4)
```

We need to exclude Antarctica and the World.
```{r}
query_5 <- "SELECT population, population_growth, birth_rate, death_rate FROM facts WHERE name IS NOT 'Antarctica' AND name IS NOT 'World'"
result_5 <- dbGetQuery(conn, query_5)

shaped_result_5 <- result_5 %>% gather(.,key =  variables, value = "value")
options(scipen=10000)
ggplot(data = shaped_result_5) + aes(x = value) + geom_histogram() + facet_wrap(~variables)

x_var <- colnames(result_5)

result_hist <- function(x){
  ggplot(data = result_5) + aes_string(x = x) + geom_histogram()
}
map(x_var, result_hist)
```

Let's find the area with the highest population density.
```{r}
query_6 <- "SELECT name, MAX((population/area) * 100) FROM facts"
result_6 <- dbGetQuery(conn, query_6)
```

I used external data. You can check the countries belonging to each continent.
```{r}
country_continent <- read_excel("country.xlsx", col_names = FALSE)
colnames(country_continent) <- c('name', 'continent')
query_7 <- "SELECT * FROM facts"
result_7 <- dbGetQuery(conn, query_7)
result_7 <- result_7 %>% left_join(country_continent, by = "name")

formed_result_7 <- result_7 %>% select(name, birth_rate, death_rate, continent) %>% 
  mutate(birth_death_rate = birth_rate/death_rate) %>% filter(!is.na(birth_rate)) %>% 
  filter(!is.na(death_rate)) %>% filter(!is.na(continent))
colSums(is.na(formed_result_7))
ggplot(data = formed_result_7) + aes(x = continent,y = birth_death_rate, fill = continent) +
  geom_boxplot()
```
 
The continent with the smallest difference between birth rate and death rate is Europe.
