---
title: "Finding the Best Markets to Advertise In"
author: "Yunsang Hwang"
output: html_document
---

read liarary and csv file
```{r}
library(readr)
library(dplyr)
library(ggplot2)
survey_data_2017<- read_csv("2017-fCC-New-Coders-Survey-Data.csv")
dim(survey_data_2017)
head(survey_data_2017, 5)
```
I tried using 
prop.table (table (survey_data_2017 $ JobRoleInterest, useNA = "ifany")) * 100 
but I was not satisfied. So I use this:

```{r}
survey_data_2017 %>% 
  group_by(JobRoleInterest) %>% 
  summarise(freq = n() * 100 / nrow(survey_data_2017)) %>%
  arrange(desc(freq))
```

There are many n / a. 
Many people are interested in web developers. 
Many people are interested in more than one role.

```{r}
droped_na_Role <- tidyr::drop_na(survey_data_2017, JobRoleInterest)
number_of_Role <- droped_na_Role %>% 
  select(JobRoleInterest) %>% rowwise %>%
  mutate(split_Roll = length(stringr::str_split(JobRoleInterest, ",")[[1]]))
number_of_Role <- number_of_Role %>% 
  ungroup() %>% 
  group_by(split_Roll) %>%
  summarise(freq = n() * 100 / nrow(number_of_Role))
as.data.frame(number_of_Role)
```


```{r}
ggplot(data = number_of_Role, aes(x = split_Roll, y = freq)) + 
  geom_histogram(stat = "identity") +
  geom_text(aes(label = round(freq, 2), y= 0.5 * freq), size = 3)
```


The focus of our courses is on web and mobile development. 
How many people are interested in at least one of these two subjects?
```{r}
web_or_mobile <- stringr::str_detect(survey_data_2017$JobRoleInterest, 
                         "Web Developer|Mobile Developer")
freq<- table(web_or_mobile)
freq <- freq * 100 / sum(freq)
freq
```

```{r}
df <- tibble::tibble(x = c("other interest", "web or mobile developer"), y = freq )
ggplot(data = df, aes(x = x, y = y, fill = x)) +
  geom_histogram(stat = "identity") +
  geom_text(aes(label = round(y, 2), y= 0.5 * y), size = 3)
```


More than 44% of customers in the United States. 
Followed by India, the United Kingdom, and Canada.

```{r}
survey_data_2017 <- survey_data_2017 %>% tidyr::drop_na(JobRoleInterest)
survey_data_2017 %>% 
  group_by(CountryLive) %>% 
  summarise(freq = n(), perc = n() * 100 / nrow(survey_data_2017)) %>%
  arrange(desc(perc))
```



```{r}
survey_data_2017 <- survey_data_2017 %>% 
  mutate(MonthsProgramming, replace(MonthsProgramming, MonthsProgramming == 0, 1)) %>%
  mutate(money_per_month = round(MoneyForLearning/MonthsProgramming, 0))
survey_data_2017 %>% summarise(number_of_na = sum(is.na(money_per_month)))
na_droped_data <- survey_data_2017 %>% tidyr::drop_na(money_per_month)
na_droped_data <- na_droped_data %>% tidyr::drop_na(CountryLive)
na_droped_data %>% 
  group_by(CountryLive) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq))
mean_money_per <- na_droped_data %>% filter(CountryLive == "United States of America" |
                          CountryLive == "India" | 
                          CountryLive == "United Kingdom"| 
                          CountryLive == "Canada") %>%
  group_by(CountryLive) %>%
  summarise(mean = mean(money_per_month)) %>%
  arrange(desc(mean))
country_4 <- na_droped_data %>% 
  filter(CountryLive == "United States of America" |
                          CountryLive == "India" | 
                          CountryLive == "United Kingdom"| 
                          CountryLive == "Canada")
country_4 <- country_4 %>% mutate(nrow = row_number())
```


```{r}
ggplot(data = country_4, aes(x = CountryLive, y = money_per_month)) +
  geom_boxplot() +
  labs(title = "money per month by country", x = "Country", y = "money_per_month") +
  theme_bw()
```

Remove outliers

```{r}
survey_data_2017 <- survey_data_2017 %>% filter(money_per_month < 20000)
countries_mean <- survey_data_2017 %>%
  filter(CountryLive == "United States of America"| 
         CountryLive == "Canada" | 
         CountryLive == "United Kingdom" |
         CountryLive == "India") %>%
  group_by(CountryLive) %>%
  summarise(mean = mean(money_per_month)) %>% 
  arrange(desc(mean))

countries_mean
```


```{r}
country_4 <- survey_data_2017 %>% 
  filter(CountryLive == "United States of America"| 
         CountryLive == "Canada" | 
         CountryLive == "United Kingdom" |
         CountryLive == "India") %>%
  mutate(index = row_number())

```

```{r}
ggplot(data = country_4, aes(x = CountryLive, y = money_per_month)) +
  geom_boxplot() +
  labs(title = "money per month by country", x = "Country", y = "money_per_month") +
  theme_bw()
```



```{r}
india <- country_4 %>% 
  filter(CountryLive =="India" & money_per_month >= 3000) 
india

usa <- country_4 %>% 
  filter(CountryLive == "United States of America" & 
         money_per_month >= 6000)
usa
us_no_bootcamp <- country_4 %>%
  filter(CountryLive == "United States of America" & 
         money_per_month >= 6000 & AttendedBootcamp == 0)
us_less_than_3 <- country_4 %>%
  filter(CountryLive == "United states of America" &
         money_per_month >= 6000 & MonthsProgramming <= 3)

canada <- country_4 %>%
  filter(CountryLive == "Canada" & money_per_month >= 4000 & MonthsProgramming <= 3)

country_4 <- country_4 %>%
  filter(!(index %in% india$index)) %>% 
  filter(!(index %in% usa$index)) %>%
  filter(!(index %in% us_no_bootcamp$index)) %>%
  filter(!(index %in% us_less_than_3$index)) %>%
  filter(!(index %in% canada$index))

```


we should advertise in is the US. 
And Canada is the second potential market.
```{r}
country_4 %>% 
  group_by(CountryLive) %>% 
  summarise(mean = mean(money_per_month)) %>%
  arrange(desc(mean))
  
ggplot(data = country_4, aes(x = CountryLive, y = money_per_month)) +
  geom_boxplot() +
  labs(title = "money per month by country", x = "Country", y = "money_per_month") +
  theme_bw()

country_4 %>% 
  group_by(CountryLive) %>%
  summarise(freq = n() * 100 / nrow(country_4)) %>%
  arrange(desc(freq))
country_4 %>%
  group_by(CountryLive) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq))

```

